BioTime

### 2019-04-17 biotime.Rmd
Don't join on NAs.
Exclude old taxonomy columns from trait data, preserve just original sci name and common name columns.

biotime_data <- biotime_ids %>%
  select(id = acceptedNameUsageID,input) %>%
  distinct() %>%
  right_join(data, by = c("input" = "genus_species")) %>%
  rename(genus_species = input)
```

@@

bird_trait_data <- bird_ids  %>%
  select(acceptedNameUsageID, input) %>%
  distinct() %>%
  right_join(bird_trait, by = c("input" = "scientific")) %>%
  rename(scientific = input)
```

@@

Are there any studies for which we have trait data for all species?
```{r}
bird_data <- biotime_data %>%
  filter(taxa == "Birds") %>%
  left_join(bird_ids)
```

>>>>

biotime_data <- biotime_ids %>%
  select(id = acceptedNameUsageID,input, scientificName) %>%
  distinct() %>%
  right_join(data %>% select(-species, -genus), by = c("input" = "genus_species")) %>%
  rename(originalSciName = input)
```

@@

#only want one column for old name and one column for new name, these are the old ID columns to remove
col_ex <- c("specid", "passnonpass", "iocorder", "blfamilylatin", "blfamilyenglish", "blfamsequid", "taxo")

bird_trait_data <- bird_ids  %>%
  select(id = acceptedNameUsageID, input) %>%
  distinct() %>%
  right_join(bird_trait %>% select(.dots = -col_ex), by = c("input" = "scientific")) %>%
  rename(originalSciName = input)
```

@@

Are there any studies for which we have trait data for all species?
```{r}
#join trait and biotime data
bird_data <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  rowid_to_column("row") %>%
  left_join(bird_trait_data %>% 
              select(), 
            na_matches = "never")

coverage <- bird_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(id))/n()) %>%
  arrange(desc(perc))

head(coverage)
```
